comgen-outline

### 2017-08-10 paper/comgen-paper.Rmd
working on intro

Figuring out that an object tends to have a property, an entity tends to exhibit a behavior, or a cause tends to produce an effect is crucial knowledge in an uncertain world.
Such *generalizations* can be acquired by drawing inductive inferences from observations [@Baldwin1993; @Xu2008; @Dewar2010].
Other cooperative agents can facilitate this, and learners can draw stronger inductive inferences in social learning contexts [@Csibra2009; @Tomasello1999; @Butler2012].
At around a child's first birthday, however, the mind gains access to a new, human-unique source of data: language.

@@

@@

Probabilistic models are used to describe language understanding in precise, quantitative terms [@Frank2012; @Goodman2013; @Franke2015; @Goodman2016], formalizing complex linguistic phenomena ranging from politeness [@Yoon2016] and hyperbole [@Kao2014] to metaphor [@Kao2014] and vagueness [@Lassiter2013; @Qing2014].
Such models of rational communication describe inferences listeners can draw from language; heretofore, however, this language has been limited to utterances that convey information about a specific entity or situation.
Meanwhile, the language of generalizations --- statements that extend beyond the here-and-now --- has eluded precise formalization.
<!-- The language of generalization is exceedingly difficult to formalize, however. -->
<!-- The cognitive act of generalization is naturally formalized in Bayesian cognitive models [@Tenenbaum2011]. -->
<!-- Bayesian models showcase the role of flexibly structured representations [@Kemp2007; @Kemp2008] and assumptions learners can make about the data-generating process [e.g., learning from pedagogical actions; @Shafto2012]. -->
<!-- Learning from language, however, is more challenging to formalize because of the inherent context-sensitivity of language [@Grice1975; @Clark1996; @Levinson2000]. -->

@@

>>>>

The knowledge that an object tends to have a property, an entity tends to exhibit a behavior, or a cause tends to produce an effect can be crucial in an uncertain world.
Such *generalizations* can be acquired by drawing inductive inferences from observations [@Baldwin1993; @Xu2008; @Dewar2010]. /ndg{older cites for this? hume?}
Other cooperative agents can facilitate this, and learners can draw stronger inductive inferences in social learning contexts [@Csibra2009; @Tomasello1999; @Butler2012].
At around a child's first birthday, however, the mind gains access to a new, human-unique source of data: language.

@@

[XXX first three pars are floppy. tighten.
There haven't been (many)? Formal models of generic language. Say why this is important.
To build one, we need to firsts say what a generalization is. We use the Bayesian idea that an inductive generalization can be understood in terms if probbilities.
Then we need to say how these probabilities are communicated. Use RSA...]

@@

<!-- The language of generalization is exceedingly difficult to formalize, however. -->
<!-- The cognitive act of generalization is naturally formalized in Bayesian cognitive models [@Tenenbaum2011]. -->
<!-- Bayesian models showcase the role of flexibly structured representations [@Kemp2007; @Kemp2008] and assumptions learners can make about the data-generating process [e.g., learning from pedagogical actions; @Shafto2012]. -->
<!-- Learning from language, however, is more challenging to formalize because of the inherent context-sensitivity of language [@Grice1975; @Clark1996; @Levinson2000]. -->

@@

Probabilistic models are used to describe language understanding in precise, quantitative terms [@Frank2012; @Goodman2013; @Franke2015; @Goodman2016], formalizing complex linguistic phenomena ranging from politeness [@Yoon2016] and hyperbole [@Kao2014] to metaphor [@Kao2014] and vagueness [@Lassiter2013; @Qing2014].
Such models of rational communication describe inferences listeners can draw from language; heretofore, however, this language has been limited to utterances that convey information about a specific entity or situation.
Meanwhile, the language of generalizations --- statements that extend beyond the here-and-now --- has eluded precise formalization.
